House price data in Brunei

### 2024-12-15 manuscript.qmd
Add abstract

---
title: House price data in Brunei
authors:
  - name: Haziq Jamil
    orcid: 0000-0003-3298-1010
    email: haziq.jamil@ubd.edu.bn
    url: "https://haziqj.ml"
    corresponding: true
    affiliations:
      - name: Universiti Brunei Darussalam
        id: ubd
        department: Mathematical Sciences, Faculty of Science
        address: Universiti Brunei Darussalam, Jalan Tungku Link
        city: Bandar Seri Begawan
        country: Brunei
        postal-code: BE 1410
  - name: Amira Barizah Noorosmawie
    affiliations:
      - ref: ubd        
  - name: Hafeezul Waezz Rabu
    affiliations:
      - ref: ubd
  - name: Lutfi Abdul Razak
    orcid: 0000-0003-1681-0895
    email: lutfi.razak@ubd.edu.bn
    affiliations:
      - ref: ubd              
date-modified: last-modified
abstract: |
  Abstract here.
engine: knitr
---

@@

- **Influence on economic and monetary policies**. Analysing the real estate market is crucial because the RPPI plays a key role in shaping monetary policy and assessing economic stability. Changes in RPPI signal inflationary pressures, guiding central bank decisions on interest rates. Developing a house price index using advertised prices, as explored by @rachman2019residential, aligns with practices in other countries, such as the UK’s RightMove House Price Index [@hmlandregistry2023comparing; @europeancommission.eurostat.2013handbook]. This dataset demonstrates how programmatic methods can automate what is typically a time-consuming and labor-intensive process.

>>>>

---
title: House price data in Brunei
authors:
  - name: Haziq Jamil
    orcid: 0000-0003-3298-1010
    email: haziq.jamil@ubd.edu.bn
    url: "https://haziqj.ml"
    corresponding: true
    affiliations:
      - name: Universiti Brunei Darussalam
        id: ubd
        department: Mathematical Sciences, Faculty of Science
        address: Universiti Brunei Darussalam, Jalan Tungku Link
        city: Bandar Seri Begawan
        country: Brunei
        postal-code: BE 1410
  - name: Amira Barizah Noorosmawie
    affiliations:
      - ref: ubd        
  - name: Hafeezul Waezz Rabu
    affiliations:
      - ref: ubd
  - name: Lutfi Abdul Razak
    orcid: 0000-0003-1681-0895
    email: lutfi.razak@ubd.edu.bn
    affiliations:
      - ref: ubd              
date-modified: last-modified
abstract: |
  This article introduces the first publicly available dataset for analyzing the Brunei housing market, covering 31,495 property listings from 1993 to 2024. The dataset, curated from property advertisements in newspapers and online platforms, includes key attributes such as price, location, property type, and physical characteristics, enriched with area-level spatial information. Comprehensive and historical, it complements the Brunei Darussalam Central Bank’s Residential Property Price Index (RPPI), addressing the limitations of restricted access to raw RPPI data and its relatively short timeline since 2015. Data collection involved manual transcription from archival sources and automated web scraping using programmatic methods, supported by innovative cleaning with large language models (LLMs) to structure unformatted text. The dataset enables spatial and temporal analysis, with potential applications in economics, urban planning, and real estate research. While minor limitations exist, such as potential missing values and spatial coverage bias toward the Brunei-Muara district, this dataset provides a robust foundation for exploring housing market trends and informing policy decisions.
---

@@

- **Influence on economic and monetary policies**. Analysing the real estate market is crucial because the RPPI plays a key role in shaping monetary policy and assessing economic stability. Changes in RPPI signal inflationary pressures, guiding central bank decisions on interest rates. Developing a house price index using advertised prices, as explored by @rachman2019residential, aligns with practices in other countries, such as the UK’s RightMove House Price Index [@hmlandregistry2023comparing; @europeancommission.eurostat2013handbook]. This dataset demonstrates how programmatic methods can automate what is typically a time-consuming and labor-intensive process.
